\vspace{60pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-09 design.tex
Remove unneeded files

Improvements were made by USING CDCS, (bottom-up, not top-down)!

@@

  - requires your friends to share their schedules on FB publicly and you to see their post
  - is schedule-first, not search-first
  - typically only occurs for the current semester

>>>>

From its very inception, Skedge's functionality and visual design were driven by the shortcomings of CDCS. It was built \emph{bottom-up}, not \emph{top-down}, as every aspect of the application was either made as a reaction to a particular grievance in CDCS or as the natural evolution of an existing feature. Skedge is thus rooted in \emph{usability} derived from real need, not mere conjecture along the question ``what could students want?''. Its success with students, shown in Chapter 4, demonstrates that this usability extends beyond my own standard and can fulfill the various discovered use-cases of students in general.

In this chapter, I will

@@

  - requires your friends to share their schedules on FB publicly and you to see their post

%%%%%%%%%%%%%%

  - is schedule-first, not search-first
  - typically only occurs for the current semester
